---
title: "Heights"
author: "Jessie Black"
date: "2023-03-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Galton Families Data

The GaltonFamilies data set is a data frame with 934 observations across 205 families with the following 8 observations:

- family (ID)
- father's height in inches
- mother's height in inches
- calculated "midparentHeight", or (father + 1.08*mother)/2
- the number of children in the family
- ordinal number for the current child (listed in decreasing order of height for boys and then girls)
- child's gender as a factor
- child's height in inches

The data is available from the package "HistData", and the data source is Galton's notebook, http://www.medicine.mcgill.ca/epidemiology/hanley/galton/notebook/, transcribed by Beverley Shipley in 2001.

```{r libraries}
library(tidyverse)
library(HistData)
```

```{r galton}
data("GaltonFamilies")
set.seed(1983)# for comparing to HarvardX Data Science course lectures
summary(GaltonFamilies)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
